GMSE: a general tool for management strategy evaluation

### 2017-09-18 notebook/presentation/GMSE_presentation.Rmd
Clean first draft

@@

>>>>

# [GMSE GUI](https://bradduthie.shinyapps.io/gmse_gui/)

@@

- Modular `gmse_apply()` function allowing user-supplied natural resource, observation, manager, and user models
- Stuctured populations (e.g., sex, stage)
- Multiple populations of interacting species
- Improved strategy prediction for managers and users
- Interactive decision-making with software users

<br>
<center>

![](acknowledgements.png)
